Systematic studies of correlations between different order flow harmonics in Pb--Pb collisions at $\mathbf{\sqrt{s_{\rm NN}}}$ = 2.76 TeV

### 2017-11-14 longSC.tex
IRC

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
In this paper we shortly denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$ in the transverse momentum range $0.2<p_{\rm T}<5.0$~GeV/$c$.
The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_3}.
The centrality dependence of $v_n$ for $n$ = 2--5 is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_3}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_3} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.

>>>>

As discussed in Sec.~\ref{sec:method}, the NSC($m$,$n$) observables are normalized by the product $\left<v_{m}^2\right>\left<v_{n}^2\right>$.
These products are obtained from two-particle correlations using a pseudorapidity gap of $|\Delta\eta| > 1.0$. 
In this paper we denote the $p_{\rm T}$ integrated $v_{n}\{2, |\Delta\eta|>1\}$ as $v_n$ in the transverse momentum range $0.2<p_{\rm T}<5.0$~GeV/$c$.
The individual flow harmonics $v_n$ used in calculations of the NSC observables are shown in Fig.~\ref{fig:Figure_3}.
The centrality dependence of $v_n$ for $n$ = 2--5 is shown in the left panels ((A), (B) and (C)) of  Fig.~\ref{fig:Figure_3}. The $v_n$ values ($n < 5$) are equivalent to those in \cite{Adam:2016izf}. The $5^{\mathrm{th}}$ order flow harmonic $v_5$ is shown in panel (C). The $p_{\rm T, min}$ dependence of $v_n$ for $n$ = 2--4 is shown in the right panels ((a), (b) and (c)) of Fig.~\ref{fig:Figure_3} in all centrality ranges relevant to the measured NSC($m$,$n$) observables.
